---
title: "R Notebook"
output: html_notebook
---

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

setwd("C:/Users/Branch/Documents/misc. code and homework/DSC630")
```{r install packages}
install.packages("coefplot")
install.packages("Rcmdr")
install.packages("Rtools")
install.packages("knitr")
install.packages("pastecs")
install.packages("Mmisc")
install.packages("QuantPsyc")
library(coefplot, quetly=TRUE)
library(Rcmdr)
library(Rtools)
library(knitr)
library(pastecs)
library(Mmisc)
library(QuantPsyc)
```


```{r import data}
dbdata <- data.frame(read.csv('model_data_for_R.csv', stringsAsFactors = FALSE))
head(dbdata)
```



